### 2014-06-28 analysis/context_permeability.Rmd
updated with lattest analysis

```{r message=FALSE}
source("../R/experiment_utils.R")
```

@@

We first load the data related to convergence to consensus. In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved. 
```{r results='asis',message=FALSE}
#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")

@@

#filter some things out
fcdata <- melt.data.frame(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))

@@

fcdata_table <- aggregate(data=fcdata, fcdata$value~num.networks + fcdata$network.0.k, FUN=sum)
colnames(fcdata_table) <- c("num.networks", "k", "value")

 #create a pretty table for latex
latex_table <- tabular(cast(fcdata_table, num.networks~k, value="value"))

@@

#I can also save this table to a file for later reference
latex(latex_table,file="tex/regular_convergence.tex", booktabs=T, )
```

@@

We now filter some of the variables out.
```{r message=FALSE}
#filter some things out
fedata <- melt.data.frame(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
head(fedata)

@@

#create a table with avg and sd
cast_fedata_table <- cast(data=fedata, formula=network.0.k~num.networks, c(mean, sd))

@@

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively. We look at **configurations with a number of networks > 3** since less networks require more connectivity to allow consensus to be reached 100% of the time.

>>>>

@@

We first load the data related to convergence to consensus. In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved. 
```{r results='asis',message=FALSE}
source("../R/experiment_utils.R")

#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv")

@@

```{r message=FALSE}

require(reshape2)

#filter some things out
fcdata <- melt(convergence_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("consensus-achieved"))

@@

fcdata_table <- aggregate(data=fcdata, fcdata$value~fcdata$num.networks + fcdata$network.0.k, FUN=sum)
colnames(fcdata_table) <- c("num.networks", "k", "value")

require(reshape)
 #create a pretty table for latex
table <- cast(fcdata, num.networks~network.0.k, sum)

require(tables)
latex_table <- tabular.cast_df(table)

@@

#I can also save this table to a file for later reference
Hmisc::latex(latex_table, file="tex/regular_convergence.tex",booktabs=T)
```

@@

We now filter some of the variables out.
```{r message=FALSE}

#filter some things out
fedata <- melt(encounter_data,id.vars=c("cfg.id","run","num.networks","network.0.k"), measure.vars=c("total-encounters"))
head(fedata)

@@

require(reshape)
#create a table with avg and sd
cast_fedata_table <- cast(data=fedata, formula=network.0.k~num.networks, c(mean, sd))

fedata_table_full <- tabular.cast_df(cast_fedata_table)
```

@@

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively. We look at **configurations with a number of networks > 3** since less networks tab1 <- tabular(Heading()*RowFactor(rowFactor2, spacing = 1, 
                        levelnames = c("rowLabel1", "rowLabel2"))*
                Heading()*RowFactor(rowFactor1, 
                        levelnames = c("b1", "b2")) ~ 
                Heading()*Factor(colFactor2, 
                        levelnames = c("colLabel1", "colLabel2") )*
                Heading()*Factor(colFactor1, 
                        levelnames = c("a1", "a2"))*
                Heading()*(x)*Heading()*(mean), 
        data = mydf)require more connectivity to allow consensus to be reached 100% of the time.

### 2014-06-28 analysis/context_switching.Rmd
updated with lattest analysis

###2 10-Regular Networks###
```{r load-parameters}
#load some utilities
source("../R/experiment_utils.R")

#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name="../data/context_switching/switching_span/2 10-regular networks/param-space_2014-06-17_15:44:50experiment:10_.csv")

@@

encounter_data <- fread("../data/context_switching/switching_span/2 10-regular networks/num_encounters.csv")
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

@@

encouters_contour <- create_contour_span(span = agg_encounters, brks = brks, guide_title = guide_title)
encouters_contour
gc()
```

```{r fig.width=16, message=FALSE}
#reshape the data to display average number of encounters
encounter_table <- dcast(data=melted_encounters, network.0.cs~network.1.cs, mean)

@@

xlab<-"\n\nSwitching for Network 1"
ylab<-"\n\nSwitching for Network 2"
zlab<-"\n\n\n Avg. Encounters"

par(mfrow=c(1,3))
plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = encounter_matrix, breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
plot_persp_span(x = seq(0.2,1,0.05), y = seq(0.2,1,0.05),data_matrix = encounter_matrix[-c(1:4),-c(1:4)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
plot_persp_span(x = seq(0.4,1,0.05), y = seq(0.4,1,0.05),data_matrix = encounter_matrix[-c(1:8),-c(1:8)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)
gc()
```

```{r fig.width=10}
par(mfrow=c(1,1))
plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = log(encounter_matrix), breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab=zlab,pallete="PRGn")
```
**Note** I don't need custom breaks, its simpler to apply a logarithm to a set of n numbers, normalize them inside the plotting function and multiply this by the maximum value in the dataset, this will get the effect I'm looking for in both the filling and contour lines.

###2 Scale-Free Networks with D=1###

###1 10-Regular + 1 Scale-Free with D=1###

>>>>

The analysis for each context switching probability span is as follows: 
```{r load-parameters}
analyse_contour <- function(paramfile, encountersfile, net1label, net2label){
  #load some utilities
source("../R/experiment_utils.R")

#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name=paramfile)

@@

encounter_data <- fread(encountersfile)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

@@

encouters_contour <- create_contour_span(span = agg_encounters, brks = brks, guide_title = guide_title,xlab=net1label, ylab=net2label)
pdf(paste("./pdf/",output_prefix,"_switching_contour.pdf"), width=7, height=5)
par(mfrow=c(1,1))
print(encouters_contour)

dev.off() 
print(encouters_contour)
gc()
}

analyse_persp <- function(paramfile, encountersfile,output_prefix,net1label,net2label){
    #load some utilities
source("../R/experiment_utils.R")

#Read the Parameters for this experiment
params <- read.exp.parameters(param_file_name=paramfile)

encounter_data <- fread(encountersfile)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.1.cs"), measure.vars=c("total-encounters"))
head(melted_encounters)
  #reshape the data to display average number of encounters
encounter_table <- dcast(data=melted_encounters, network.0.cs~network.1.cs, mean)

@@

xlab<- net1label
ylab<- net2label
zlab<-"\n\n\n Avg. Encounters"

pdf(paste("./pdf/",output_prefix,"_switching_persp.pdf"), width=15, height=5)
par(mfrow=c(1,3))
plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = encounter_matrix, breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)

plot_persp_span(x = seq(0.2,1,0.05), y = seq(0.2,1,0.05),data_matrix = encounter_matrix[-c(1:4),-c(1:4)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)

plot_persp_span(x = seq(0.4,1,0.05), y = seq(0.4,1,0.05),data_matrix = encounter_matrix[-c(1:8),-c(1:8)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)

dev.off() 
par(mfrow=c(1,3))
plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = encounter_matrix, breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)

plot_persp_span(x = seq(0.2,1,0.05), y = seq(0.2,1,0.05),data_matrix = encounter_matrix[-c(1:4),-c(1:4)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)

plot_persp_span(x = seq(0.4,1,0.05), y = seq(0.4,1,0.05),data_matrix = encounter_matrix[-c(1:8),-c(1:8)], breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab = zlab)

zlab<-"\n\n\n Log(Avg. Encounters)"
pdf(paste("./pdf/",output_prefix,"_switching_log_persp.pdf"), width=5, height=5)
plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = log(encounter_matrix), breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab=zlab,pallete="PRGn")
dev.off()
plot_persp_span(x = seq(0,1,0.05), y = seq(0,1,0.05),data_matrix = log(encounter_matrix), breaks=log(c(1:10)),xlab=xlab,ylab=ylab,zlab=zlab,pallete="PRGn")
}
```

###2 10-Regular Networks###
```{r}
params <- "../data/context_switching/switching_span/2 10-regular networks/param-space_2014-06-17_15:44:50experiment:10_.csv"
encounters <- "../data/context_switching/switching_span/2 10-regular networks/num_encounters.csv"

output_prefix <- "context_switching_2_10_regular"

net1label <- "\n\nSwitching for Network 1 \n regular network, k=10"
net2label <- "\n\nSwitching for Network 2 \n regular network, k=10"

analyse_contour(params, encounters,net1label,net2label)
```

```{r fig.width=15}
analyse_persp(params, encounters,output_prefix,net1label,net2label)
```

**Note** I don't need custom breaks for the **persp plots**, its simpler to apply a logarithm to a set of n numbers, normalize them inside the plotting function, and multiply this by the maximum value in the dataset, this gets me the effect I'm looking for both the filling and contour lines.

###2 30-Regular Networks###
```{r}
params <- "../data/context_switching/switching_span/2 30-regular networks/param-space_2014-06-20_20:25:18experiment:10_.csv"
encounters <- "../data/context_switching/switching_span/2 30-regular networks/num_encounters.csv"
output_prefix <- "context_switching_2_30_regular"

net1label <- "\n\nSwitching for Network 1 \n regular network, k=30"
net2label <- "\n\nSwitching for Network 2 \n regular network, k=30"

analyse_contour(params, encounters,net1label,net2label)
```
As we can see, increasing the connectivity of the agents makes so that the switching probability values are no longer as important to the speed of convergence to total concensus. The clustering coefficient for the merged networks is significantly higher for k = 30 than for k = 10. This is especially true for a number of networks = 2 (see [network properties](http://rpubs.com/davidelnunes/socsim_network_properties)). The average path length is also lower for k=30 although this difference is not as drastic (for 2 networks) as in the clustering coefficient.

```{r fig.width=15}
analyse_persp(params, encounters,output_prefix,net1label,net2label)
```

###2 Scale-Free Networks with D=1###
```{r}
params <- "../data/context_switching/switching_span/2 scale-free networks d=1/param-space_2014-06-17_15:58:29experiment:11_.csv"
encounters <- "../data/context_switching/switching_span/2 scale-free networks d=1/num_encounters.csv"
output_prefix <- "context_switching_2_sf_d1"

net1label <- "\n\nSwitching for Network 1 \n scale-free network, d=1"
net2label <- "\n\nSwitching for Network 2 \n scale-free network, d=1"

analyse_contour(params, encounters,net1label,net2label)
```

```{r fig.width=15}
analyse_persp(params, encounters,output_prefix,net1label,net2label)
```

###2 Scale-Free Networks with D=5###
```{r}
params <- "../data/context_switching/switching_span/2 scale-free networks d=5/param-space_2014-06-25_11:38:56experiment:11_.csv"
encounters <- "../data/context_switching/switching_span/2 scale-free networks d=5/num_encounters.csv"
output_prefix <- "context_switching_2_sf_d5"

net1label <- "\n\nSwitching for Network 1 \n scale-free network, d=5"
net2label <- "\n\nSwitching for Network 2 \n scale-free network, d=5"

analyse_contour(params, encounters,net1label,net2label)
```
With 2 scale-free networks with **d=5**, similarly to the 2 k-regular networks, switching is less important to achieve faster consensus. The main difference is that the number of edges is nowhere near the number of edges of 30-regular networks for 100 agents. With the 30-regular networks we generate 30 edges per agent (a total of 3000 edges since we have 100 agents). With the scale-free, with each agent we add 5 edges, which gives us a total of 500 edges. So this effect is not related to the connectivity of the agents but rather to the properties of the underlying structure. The clustering coefficient for d=1 for instance is 0--the network is basically a forest (a set of tree graphs)--, with d=5 this is no longer the case. For d=1 the average path length of scale-frees is already lower than a regular network with k within the values [1,5].
```{r fig.width=15}
analyse_persp(params, encounters,output_prefix,net1label,net2label)
```

###1 10-Regular + 1 Scale-Free with D=1###
In this experiment, network 1 has a 10-Regular Topology while network 2 has a scale-free topology with d=1. 
```{r}
params <- "../data/context_switching/switching_span/scale-free d=1 k-regular k=10/param-space_2014-06-17_16:06:26experiment:12_.csv"
encounters <- "../data/context_switching/switching_span/scale-free d=1 k-regular k=10/num_encounters.csv"

output_prefix <- "context_switching_1_10regular_1_scale-free_d1"

net1label <- "\n\nSwitching for Network 1 \n regular network, k=10"
net2label <- "\n\nSwitching for Network 2 \n scale-free network, d=1"

analyse_contour(params, encounters,net1label,net2label)
```

```{r fig.width=15}
analyse_persp(params, encounters,output_prefix,net1label,net2label)
```

###2 10-Regular Networks with 300 Agents###

In the previous experiments we use 100 agents. This time, we use 300 agents to see the effect
of context switching with slightly diferent network properties. The scale should not be important here
but rather the conectivity pattern. I hypothesise that what influences the results the most with k-regular 
networks is **the proportion of connections (given by 2k) versus the number of agents in the network**.

```{r}
params <- "../data/context_switching/switching_span/2 10-regular networks 300 agents/param-space_2014-06-23_23:48:11experiment:10_.csv"
encounters <- "../data/context_switching/switching_span/2 10-regular networks 300 agents/num_encounters.csv"

output_prefix <- "context_switching_2_10regular_300agents"

net1label <- "\n\nSwitching for Network 1 \n regular network, k=10, 300 agents"
net2label <- "\n\nSwitching for Network 1 \n regular network, k=10, 300 agents"

analyse_contour(params, encounters,net1label,net2label)
```
We can observe that lower connectivity also means that **the lower the switching probability the more important simetry is--if the network topologies are the same for both networks**. It is the same for scale-free networks with d = 1.
```{r fig.width=15}
analyse_persp(params, encounters,output_prefix,net1label,net2label)
```

### 2 30-Regular Networks 300 Agents ###
We can see that the results for k = 30 and 300 agents are qualitatively similar to the results for k=10 and 100 agents. 
```{r}
params <- "../data/context_switching/switching_span/2 30-regular networks 300 agents/param-space_2014-06-24_01:00:58experiment:10_.csv"
encounters <- "../data/context_switching/switching_span/2 30-regular networks 300 agents/num_encounters.csv"

output_prefix <- "context_switching_2_30regular_300agents"

net1label <- "\n\nSwitching for Network 1 \n regular network, k=30, 300 agents"
net2label <- "\n\nSwitching for Network 1 \n regular network, k=30, 300 agents"

analyse_contour(params, encounters,net1label,net2label)
```

```{r fig.width=15}
analyse_persp(params, encounters,output_prefix,net1label,net2label)
```

# Results for Multiple-Networks and Comparison with Context Permeability #

## Comparison for K-Regular Networks ##
```{r}
#**************************************************************************
#   read encounter results for context permeability (for comparison)
#**************************************************************************
params <- "../data/context_permeability/regular_networks/param-space_2014-05-30_16:47:53experiment:0_.csv"
encounters <- "../data/context_permeability/regular_networks/num_encounters.csv"

params <- read.exp.parameters(param_file_name=params)

encounter_data <- fread(encounters)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
#merge with configuration context switching values
require(reshape2)
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.k","num.networks")], by="cfg.id")
head(encounter_data)
#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.k","num.networks"), measure.vars=c("total-encounters"))
head(melted_encounters)
permeability_encounters <- melted_encounters

#***************************************************************
#   read encounter results for context switching
#***************************************************************
params <- "../data/context_switching/multiple_networks/regular_networks/param-space_2014-06-22_00:33:19experiment:10_.csv"

encounters <- "../data/context_switching/multiple_networks/regular_networks/num_encounters.csv"

params <- read.exp.parameters(param_file_name=params)

encounter_data <- fread(encounters)
encounter_data <- as.data.frame(encounter_data)[,-ncol(encounter_data)]
head(encounter_data)

#merge with configuration context switching values
require(reshape2)
encounter_data <- merge(encounter_data, params[,c("cfg.id","network.0.cs","network.0.k","num.networks")], by="cfg.id")
head(encounter_data)

#melt data to use cast
melted_encounters <- melt(encounter_data,id.vars=c("cfg.id","run","network.0.cs","network.0.k","num.networks"), measure.vars=c("total-encounters"))
head(melted_encounters)

for(n in 2:5){
  #plot for 2 networks
  current_encounters<-melted_encounters[melted_encounters$"num.networks" == n,]
  perm_encounters<-permeability_encounters[permeability_encounters$"num.networks" == n,]

  plot_data <- dcast(current_encounters, network.0.k + network.0.cs ~ variable, mean)
  colnames(plot_data) <- c("k","cs","avg-encounters")

  perm_data <- dcast(perm_encounters, network.0.k ~ variable, mean)
  colnames(perm_data) <- c("k","avg-encounters")

  plot <- NULL

  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$cs), color=as.factor(plot_data$cs)),size = 3.5)
  plot <- plot +  geom_line(aes(color=as.factor(plot_data$cs), group=as.factor(plot_data$cs), linetype=as.factor(plot_data$cs)),size=1)   
  #add line for permeability baseline
  plot <- plot + geom_point(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters", shape="permeability", color="permeability"),size = 3.5)
  plot <- plot + geom_line(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters", group="Permeability", linetype="permeability", color="permeability"),size=1)

  plot <- plot + labs(color="CS", shape="CS", linetype="CS", y="Average Encounters", x="K",
                       title=paste("K-Regular Networks With Number of Networks =",n))

  print(plot)

}
gc()

for(cs in c(0.25,0.5,0.75)){
  #plot for 2 networks
  current_encounters<-melted_encounters[melted_encounters$"network.0.cs" == cs,]
  #perm_encounters<-permeability_encounters[permeability_encounters$"num.networks" > 1,]

  plot_data <- dcast(current_encounters, network.0.k + num.networks ~ variable, mean)
  colnames(plot_data) <- c("k","num-networks","avg-encounters")

  #gets too messy with permeability data 
  #perm_data <- dcast(perm_encounters, network.0.k + num.networks ~ variable, mean)
  #colnames(perm_data) <- c("k","num-networks", "avg-encounters")

  plot <- ggplot(plot_data, aes(x=as.factor(plot_data$k), y=plot_data$"avg-encounters")) 
  plot <- plot +  geom_point(aes(shape=as.factor(plot_data$"num-networks"), color=as.factor(plot_data$"num-networks")),size = 3.5)
  plot <- plot +  geom_line(aes(color=as.factor(plot_data$"num-networks"), group=as.factor(plot_data$"num-networks"), linetype=as.factor(plot_data$"num-networks")),size=1)

  #add line for permeability
  #plot <- plot +  geom_point(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters", shape="permeability", color=as.factor(perm_data$"num-networks")),size = 3.5)
  #plot +  geom_line(data=perm_data, aes(x=as.factor(perm_data$k), y=perm_data$"avg-encounters",group=as.factor(perm_data$"num-networks"),linetype=as.factor(plot_data$"num-networks"),color=as.factor(perm_data$"num-networks")),size=1)

  plot <- plot + labs(color="Num. Networks", shape="Num. Networks", linetype="Num. Networks", y="Average Encounters", x="K",
                      title=paste("K-Regular Networks With CS =",cs))

   print(plot)
}
gc()

```

### 2014-06-28 analysis/network_properties.Rmd
updated with lattest analysis

>>>>

# Properties for Scale-Free Networks #
We now look at the properties we get when we merge scale-free networks with different values of **D** (number of edges added with preferential attachement each time a new node is added to the network).

```{r}
#shows the d values explored and the number of networks
params <- read.exp.parameters("../data/context_permeability/scale-free_networks/param-space_2014-05-30_18:38:14experiment:1_.csv")
params <- params[,c("cfg.id","num.networks","network.0.d")]

#read the network data
require(bigmemory)
network_data <- read.big.matrix(filename="../data/context_permeability/scale-free_networks/networks.csv", header=T, sep=";")

#Collect the network data and create a data table to hold the network properties
require(parallel)

props <- NULL
num_networks <- c(1,2,3,4,5)
d_values <- c(1,2,3,4,5)
runs <- sort(unique(network_data[,"run"]))

require(BBmisc)#for progress bar
pb <- makeProgressBar(min=0, max=(length(num_networks)*length(d_values)), label="network analysis")

#pre-alocate a matrix for the network properties
props <- matrix(nrow=(length(num_networks)*length(d_values)*length(runs)), ncol=7)
i <- 0

for(n in num_networks){
  #reads the properties for all the k-regular networks with the given k and num_networks 
  for(d in d_values){
    cfg <- params[params$"num.network" == n & params$"network.0.d" == d,][[1]]

    props[(i+1):(i+100),] <- cbind(d,n,properties)
    i <- i + 100  
    #some progress feddback
    pb$inc(1,paste("reading n=",n,"d=",d,"\n"))
    gc()
  } 
}
pb$kill()

colnames(props)<-c("d","networks","run","nodes","edges","clustering-coefficient","average-path-length")

#clean up
rm(pb)
gc()

```

Creating boxplots to observe the average path length and the clustering coefficient, we can see that these values don't varie much within each configuration with the exception of the configuration: **d=1 networks=1**. This happens because the generative process is stochastic by nature and thus depends on the preferential attachement node selection. Within scale-free networks we can thus assume certain property values for specific combinations of networks much like what happens with the k-regular networks.

#create average path length box plots for d = 1,2,3,4,5
net_props <- props

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",fill=as.factor(net_props$d)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="D", y="Average Path Length", x="Number of Networks")
plot

#create clustering coefficient box plots for d = 1,2,3,4,5

plot <- plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",fill=as.factor(net_props$d)) ) 
plot <- plot + geom_boxplot()
plot <- plot + labs(fill="D", y="Clustering Coefficient", x="Number of Networks")
plot 
```

We now plot the average value of **average path length** and **clustering coefficient** for a total of 100 Scale-Free Networks. We analyse the properties of networks with different levels of **D**.

apl_data <- melt(props, id=c("d","networks","run"),measure.vars=c("average-path-length"))
clustering_data <- melt(props, id=c("d","networks","run"),measure.vars=c("clustering-coefficient"))

average_apl_data <- dcast(apl_data, d + networks ~ variable, mean)
average_clustering_data <- dcast(clustering_data, d + networks ~ variable, mean)

#plot average path length for d = 1,2,3,4,5
net_props <- average_apl_data
plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"average-path-length",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$d), color=as.factor(net_props$d)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
plot <- plot + labs(color="D", shape="D", linetype="D", y="Average Path Length", x="Number of Networks")
plot

```{r}
#plot for D = 1,2,3,4,5
net_props <- average_clustering_data

plot <- ggplot(net_props, aes(x=as.factor(net_props$networks), y=net_props$"clustering-coefficient",)) 
plot <- plot +  geom_point(aes(shape=as.factor(net_props$d), color=as.factor(net_props$d)),size = 3.5)
plot <- plot +  geom_line(aes(color=as.factor(net_props$d), group=as.factor(net_props$d), linetype=as.factor(net_props$d)),size=1)   
plot <- plot + labs(color="D", shape="D", linetype="D", y="Clustering Coefficient", x="Number of Networks")
plot
